Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-19 doc/main_jfm.tex
started mods to Section 4

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Jeffery Orbit}
The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\Theta = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,

\begin{equation}
\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratios of the particle are $2$ and $3$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from the Jeffery orbits.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
  \caption{Comparisons of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure. Here two cases of aspect ratio are validated, $a/b = 2$ and $a/b=3$.
  }
    \label{figure1}
\end{figure}

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}
%
\usepackage[justification=justified]{caption}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Jeffery Orbit}
We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
A single elliptical particle is suspended in the fluid with center at the origin.
The Jeffrey orbit  
\begin{equation}
\label{eq:jeff}
\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
\end{equation}
gives the angle between the major axis and $\mathbf{e}_2$
where $a$, $b$ are the semi-major and semi-minor axes. 
We are assuming $\Theta(0) = 0$.
Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
    \label{figure1}
\end{figure}
